\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-27 paper/submission.tex
corrected a typo in one of the bibitems in submission.tex

\bibitem{dissent} H.~Corrigan-Gibbs, B.~Ford, In: A.~D.~Keromytis and 
V.~Shmatikov (Eds.), $17^{th}$ Conference on Computer and Communications 
Security, Oct. 4-8, 2010, Chicago, USA (ACM, New York, 2010)

>>>>

\bibitem{dissent} H.~Corrigan-Gibbs, B.~Ford, In: A.~D.~Keromytis and 
V.~Shmatikov (Eds.), $17^{th}$ Conference on Computer and Communications 
Security, October 4-8, 2010, Chicago, USA (ACM, New York, 2010)
